\section{Discussion}
\label{sec:Discussion}

\subsection{Depletion voltage}

In the first part, the depletion voltage is determined to be $\qty{60}{\volt}$.
Later, the depletion voltage is again measured by using the charge collection efficiency.
In this case, a value of $\qty{80}{\volt}$ is obtained. The manufacturer \cite{V15} states a deplition
voltage in the range of $\qty{60}{}$ to $\qty{80}{\volt}$, so both measurements are
acceptable. Both values are only estimations, as they are obtained by roughly determining the
point where a curve flattens into a plateau. Therefore it is not unexpected that they dont fully agree.

\subsection{Measuring the strip sensors}

The pitch of the strip sensors has been calculated from their measured width and distance to be
$\qty{160}{\micro\meter}$. This is the exact value given by the manufacturer \cite{V15}, the high
precision could be archieved through the $\qty{10}{\micro\meter}$ resolution chosen for the scan.
The lasers extension was measured at $\qty{50}{\micro\meter}$ and is thus significantly larger
than the stated \cite{V15} $\qty{20}{\micro\meter}$. This indicates that the laser probably was not
fully focused during the measurement, which is to be excpected as it prooved difficult to find an
absolout maxima when adjusting the horizontal micrometer scew.

The charge collection efficiency curve shows a behaviour close to the theoretical one, with the
exception that the plateau slighty increases for voltages above the depletion voltage. This might be
a consequence of noise that increases with the bias voltage and is not fully removed from the data.

The value for the penetration depth $ a= \qty{253+-6}{\micro\meter}$ seems consistent with the sensor
thickness of $D = \qty{300}{\micro\meter}$ and the given pentration depths of lasers with slightly different
wavelenghts in \cite{V15}.

\subsection{Energy spectrum}

During the large source scan, the calculated energy spectrum resembles the expected convolution of a
Landau and Gauss distribution \cite{V15}, where the most probable energy is lower than the mean energy.
Using the modified Bethe-Bloch equation, it can be calculated that the average energy disposition 
of an ionising electron of the maximum energy of the primary decay of $^{90}\text{Sr}$ in pure silicon is
$\qty{3.88}{\mega\electronvolt\per\centi\meter}$.
Multiplying this by the sensor thickness $D$, the theoretically expected mean energy loss becomes
$\bar{E}_{\text{theo}} = \qty{116.4}{\kilo\electronvolt}$. This can be compared this to the measured
mean energy loss
\begin{align*}
    \bar{E}_{\text{theo}} &= \qty{116.4}{\kilo\electronvolt} \\
    \bar{E}_{\text{exp}} &= \qty{163}{\kilo\electronvolt}\, .
\end{align*}
A deviation of $\qty{28.6}{\percent}$ is observed, which is quite large. A possible reason might be an underestimation
of the noise in the sensor, also the modified Bethe-Bloch equation is only an approximation with limited
precision.